# Data understanding and preparation

```{r setup, include = FALSE}
source(here::here("script/setup.R"))
```

## Dataset

```{r, warning = FALSE}
# Upload the data
setwd(here::here("data/"))
GermanCreditRaw <- read_csv2("GermanCredit.csv")
```

To create a model that will predict whether a client application represents a risk or not, we work on a dataset from our client containing data on `r nrow(GermanCreditRaw)` past credit applications, described by the following variables:

- **CHK_ACCT**: The checking account status of the applicant in Deutsche Mark (DM).

- **DURATION**: The duration of the credit in months.

- **HISTORY**: The credit history of the applicant.

- **NEW_CAR**: Purpose of the credit.

- **USED_CAR**: Purpose of the credit.

- **FURNITURE**: Purpose of the credit.

- **RADIO/TV**: Purpose of the credit.

- **EDUCATION**: Purpose of the credit.

- **RETRAINING**: Purpose of the credit.

- **AMOUNT**: The credit amount.

- **SAV_ACCT**: The average balance in savings account in Deutsche Mark (DM).

- **EMPLOYMENT**: If the applicant is employed and since how long.

- **INSTALL_RATE**: The installment rate as percentage of disposable income.

- **MALE_DIV**: If the applicant is male and divorced.

- **MALE_SINGLE**: If the applicant is male and single.

- **MALE_MAR_or_WID**: If the applicant is male, married or widowed.

- **CO_APPLICANT**: If the applicant has a co-applicant.

- **GUARANTOR**: If the applicant has a guarantor.

- **PRESENT_RESIDENT**: If the applicant is a resident and since how many years.

- **REAL_ESTATE**: If the applicant owns real estate.

- **PROP-UNKN-NONE**: If the applicant owns no property (or unknown).

- **AGE**: Age of the applicant.

- **OTHER_INSTALL**: If the applicant has other installment plan credit.

- **RENT**: If the applicant rents.

- **OWN_RES**: If the applicant owns residence.

- **NUM_CREDITS**: Number of existing credits of the applicant at our client bank.

- **JOB**: The nature of the applicant's job.

- **NUM_DEPENDENT**: Number of people for whom liable to provide maintenance.

- **TELEPHONE**: If the applicant has a phone in his or her name.

- **FOREIGN**: If the applicant is a foreign worker.

- **RESPONSE**: If the credit application is rated as "Good" or "Bad".

## Exploratory Data Analysis

In this part, we thoroughly explore the dataset to get a better understanding.

### Inacurracies

By doing an exploratory data analysis, we find some inaccuracies and in agreement with our client, we change them as follow:

- One observation of the variable "AGE": 75 instead of 125 years old.
- One observation of the variable "EDUCATION": 1 instead of -1.
- One observation of the variable "GUARANTOR": 1 instead of 2.

```{r}
# Removing the first column, aka "OBS#", because not useful.
GermanCredit <- GermanCreditRaw %>% 
  select(-c("OBS#"))

# Renaming the variables:
names(GermanCredit)[names(GermanCredit) == 'RADIO/TV'] <- 'RADIO_TV'
names(GermanCredit)[names(GermanCredit) == 'CO-APPLICANT'] <- 'CO_APPLICANT'
```

```{r}
# First inaccuracy: one observation of the column age is miscoded.
GermanCredit <- GermanCredit %>% 
  mutate(AGE = replace(AGE, AGE == 125, 75))

# Second inaccuracy: one observation of the column education is miscoded
GermanCredit <- GermanCredit %>% 
  mutate(EDUCATION = replace(EDUCATION, EDUCATION == -1, 1))

# Third inaccuracy: one observation of the column guarantor is miscoded
GermanCredit <- GermanCredit %>% 
  mutate(GUARANTOR = replace(GUARANTOR, GUARANTOR == 2, 1))
```

Then, we separated the database in 2 parts: the first part consider only the good clients, and the second part consider only the bad clients. 
```{r}
# GermanCredit accepted
YES_GC <- filter(GermanCredit,RESPONSE=="1")
```

```{r}
# GermanCredit refused
NO_GC <- filter(GermanCredit,RESPONSE=="0")
```

### Unbalanced observations

One interesting point is that the dataset is heavily unbalanced: 700 credit applications rated as good versus 300 credit applications rated as bad. We will need to balance the dataset for our modelling.

```{r, echo = FALSE, results = 'hide'}
table(GermanCredit$RESPONSE)
```

```{r, message=FALSE}
# Distribution of the grade per credit applications
GermanCredit %>% 
  ggplot(aes(x = as.factor(RESPONSE), fill=as.factor(RESPONSE))) +
  geom_bar() +
  labs(title = "Number of credit applications per grade",
       y = "Number",
       x = "Grade") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

To have a better visualization of our variables. We did some boxplot which show the distribution of the data. 

```{r, results = 'hide'}
# Distribution of the continuous variables, i.e. duration, amount, age

# Here duration

p.duration <- GermanCredit %>% 
  ggplot(aes(x = DURATION, y = as.factor(RESPONSE), fill = as.factor(RESPONSE))) +
  geom_boxplot() +
  labs(title = "Duration of the credit applications per grade",
       x = "Months",
       y = "Grade") +
  scale_y_discrete(label=c("0"="Bad", "1"="Good")) +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# Amount

p.amount <- GermanCredit %>% 
  ggplot(aes(x = AMOUNT, y = as.factor(RESPONSE), fill=as.factor(RESPONSE))) +
  geom_boxplot() +
  labs(title = "Amount of the credit applications per grade",
       x = "DM",
       y = "Grade") +
  scale_y_discrete(label=c("0"="Bad", "1"="Good")) +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# Age

p.age <- GermanCredit %>% 
  ggplot(aes(x = AGE, y = as.factor(RESPONSE), fill=as.factor(RESPONSE))) +
  geom_boxplot() +
  labs(title = "Age of the credit applicants",
       x = "Years",
       y = "Grade") +
  scale_y_discrete(label=c("0"="Bad", "1"="Good")) +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, fig.show='hide'}
figure1 <- ggarrange(p.duration, p.age, p.amount,
                    labels = c("A", "B", "C"),
                    ncol = 2, nrow = 2)
figure1
```
This first boxplot A shows that bad clients mostly asked for longer duration credit than good clients. This could be a raison why they received a refusal. The second boxplot B shows that the age of clients doesn not seem to be a key criteria but the amount of the credit (boxplot C) seems to be more important as most of the good clients asked for a smaller amount. 

Then, we explored the distribution of the financial variables.
```{r}
# Let's explore the distribution of the categorical variables
#CHK_ACCT
p.chkacct <- GermanCredit %>% 
  ggplot(aes(x = CHK_ACCT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Status of the checking account per grade",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#HISTORY
p.history <- GermanCredit %>% 
  ggplot(aes(x = HISTORY, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grades related to the history of past credits",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# SAV_ACCT
p.savacct <- GermanCredit %>% 
  ggplot(aes(x = SAV_ACCT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grades in regard with the average balance in saving accounts",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#NUM_CREDIT
p.numcre <- GermanCredit %>% 
  ggplot(aes(x = NUM_CREDITS, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to the number of credits",
       x = "Number of credits",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, fig.show='hide'}
figure_fin <- ggarrange(p.history, p.savacct, p.numcre, p.chkacct,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_fin
```

The first graph A present the situation with past credits. The behavior for good and bad clients is almost the same which does not allow us to make a clear difference. On the graph B we can see that most of the clients have small savings of even no savings at all. Most of the clients have already 1 or 2 credits at this bank. Almost none of them ask for a third or fourth credit. 
On the histogram D we see that the amount of money on the account not so important. Indeed, most of the good client do not even have a checking account. 

The graphs below displays fournitures and products owned by the clients. 

```{r}
# NEW_CAR
p_newcar <- GermanCredit %>% 
  ggplot(aes(x = as.factor(NEW_CAR), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a new car",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# USED CAR
p_usedcar <- GermanCredit %>% 
  ggplot(aes(x = as.factor(USED_CAR), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a used car",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# FURNITURE
p_fur <- GermanCredit %>% 
  ggplot(aes(x = as.factor(FURNITURE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a furniture",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# RADIO/TV
p_radtv <- GermanCredit %>% 
  ggplot(aes(x = as.factor(RADIO_TV), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a radio/tv",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, fig.show='hide'}
figure_prod <- ggarrange(p_newcar, p_usedcar, p_fur, p_radtv,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_prod
```
Most of the time the credits are not very favorable to finance products. However, new cars are more appreciated by banks than used cars and radio/tv are more financed than furnitures. 

```{r}
# EMPLOYMENT
p.empl <- GermanCredit %>% 
  ggplot(aes(x = EMPLOYMENT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade with regard to employment duration",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#JOB
p.job <- GermanCredit %>% 
  ggplot(aes(x = JOB, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to the nature of jobs",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# EDUCATION
p_edu <- GermanCredit %>% 
  ggplot(aes(x = as.factor(EDUCATION), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for education",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# RETRAINING
p_ret <- GermanCredit %>% 
  ggplot(aes(x = as.factor(RETRAINING), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for retraining",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, fig.show='hide'}
figure_pro <- ggarrange(p.empl, p.job, p_edu, p_ret,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_pro
```

As we can see on the graph before, most of the time, if the client ask a credit to pay education, the bank will refuse, even if the client is good. It is slightly the same for retraining. Most of the good client have a job for more than a year and are skilled employees. 

```{r}
# PRESENT_RESIDENTS
p.preres <- GermanCredit %>% 
  ggplot(aes(x = PRESENT_RESIDENT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to residents duration stays",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# INSTALLMENT_RATE
p.insrat <- GermanCredit %>% 
  ggplot(aes(x = INSTALL_RATE, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade per installment rate",
       x = "% of disposable income",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#REAL ESTATE
p_reaest <- GermanCredit %>% 
  ggplot(aes(x = as.factor(REAL_ESTATE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if own real estate",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#PROP_UNKN_NONE
p_prop <- GermanCredit %>% 
  ggplot(aes(x = as.factor(PROP_UNKN_NONE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if own no property or unknown",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#OWN_RES
p_ownres <- GermanCredit %>% 
  ggplot(aes(x = as.factor(OWN_RES), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if owns residence",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#GUARANTOR
p_gua <- GermanCredit %>% 
  ggplot(aes(x = as.factor(GUARANTOR), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if guarantor",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# APPLICANT RENTS
p_apprent <- GermanCredit %>% 
  ggplot(aes(x = as.factor(RENT), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if rent",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, fig.show='hide'}
figure_reales1 <- ggarrange(p.preres, p.insrat, p_reaest, p_prop, p_ownres, p_gua, p_apprent,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_reales1
```

The graph A presents the qualification of client depending of the duration stays in their home. This criteria does not seem to be really indicative even if the most good clients live in their place since more than 4 years. The installment rate does not seem to impact the qualification of the client neither as most of the good and bad clients are rated by 4 (see graph B). Owning a real estate is not the key to be perceived as a good client neither. As the graph C prove, a lot of good clients do not have any real estate. But at the opposite having no property is a bad situation in the case of asking for a credit. 

```{r, fig.show='hide'}
figure_reales2 <- ggarrange(p_ownres, p_gua, p_apprent,
                    labels = c("E", "F", "G"),
                    ncol = 2, nrow = 2)
figure_reales2
```

The graphs show that most of the good clients own their residence and not rent but a guarantor is definitely not a must. 


```{r}
# MALE_DIV
p_maldiv <- GermanCredit %>% 
  ggplot(aes(x = as.factor(MALE_DIV), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if male and divorced",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#MALE_SINGLE
p_malsin <- GermanCredit %>% 
  ggplot(aes(x = as.factor(MALE_SINGLE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if male and single",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# MALE_MAR_or_WID
p_malmarwid <- GermanCredit %>% 
  ggplot(aes(x = as.factor(MALE_MAR_or_WID), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if male married or widowed",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#FOREIGN
p_for <- GermanCredit %>% 
  ggplot(aes(x = as.factor(FOREIGN), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if foreign workers",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

```

```{r, fig.show='hide'}
figure_demo <- ggarrange(p_maldiv, p_malsin, p_malmarwid, p_for,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_demo
```
About the demographic data of an applicant, clients are generally not male and single and not foreign workers. 

```{r}
#CO APLLICANT
p_coapp <- GermanCredit %>% 
  ggplot(aes(x = as.factor(CO_APPLICANT), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if co-applicant",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#OTHER INSTALL
p_otherinstall <- GermanCredit %>% 
  ggplot(aes(x = as.factor(OTHER_INSTALL), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if other installment plan",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#NUM_DEPENDENT
p.numdep <- GermanCredit %>% 
  ggplot(aes(x = as.factor(NUM_DEPENDENTS), fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to the number of dependent",
       x = "Number of people for whom liable to provide maintenance",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#TELEPHONE
p_tel <- GermanCredit %>% 
  ggplot(aes(x = as.factor(TELEPHONE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if telephone on his name",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, fig.show='hide'}
figure_other <- ggarrange(p_coapp, p_otherinstall,p.numdep, p_tel,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_other
```
The population of clients basically do not have co-applicants and they do not have other installment plan neither for majority of them. The name's telephone does not seem to be important as a lot of clients have and have not the telephone on their name. However, most of the clients are not liable to provide maintenance. 

```{r, results='hide'}
setwd(here::here("data/"))
write_csv(GermanCredit, "GermanCreditClean.csv")
```

We can see below the mean of good clients and the mean of bad clients. It is important to keep in account that the sample of good clients is much higher than the number of bad clients. 
```{r, include=FALSE}
# let's check if old people have basically more credit than young people
mean_yes<-mean(YES_GC$AGE)
mean_yes

mean_no<-mean(NO_GC$AGE)
mean_no

# age does not seem to be a key criterion 
```

The matrix below present the correlations between variables. To read in a easiest way, we separated the variables in categories. As before, the categories were created based on their area. 
```{r}
# correlation matrix

#head(YES_GC)
#corgc <- cor(GermanCredit)
#corgc

#creation of a new dataset
cordata_fin <- GermanCredit[, c("CHK_ACCT", "HISTORY", "AMOUNT", "SAV_ACCT", "NUM_CREDITS", "RESPONSE") ] 
ggpairs(cordata_fin, title="Correlogram on financial data")

cordata_own <- GermanCredit[, c("NEW_CAR", "USED_CAR", "FURNITURE", "RADIO_TV", "RESPONSE") ]
ggpairs(cordata_own, title="Correlogram on owned products data")

cordata_pro <- GermanCredit[, c("JOB", "EDUCATION", "RETRAINING", "EMPLOYMENT", "RESPONSE") ] 
ggpairs(cordata_pro, title="Correlogram on professional data")

cordata_immo <- GermanCredit[, c("INSTALL_RATE", "REAL_ESTATE", "PRESENT_RESIDENT", "PROP_UNKN_NONE", "RENT", "OWN_RES", "RESPONSE") ]
ggpairs(cordata_immo, title="Correlogram on real estate data")

cordata_demo <- GermanCredit[, c("MALE_DIV", "MALE_SINGLE", "MALE_MAR_or_WID", "AGE", "FOREIGN", "RESPONSE") ] 
ggpairs(cordata_demo, title="Correlogram on demographic data")

#cor<-ggpairs(GermanCredit, title="correlogram with ggpairs()") 
```

The following part of the project is focus on defining a typical profile of a good client. The goal is to define an average good client based on the average of all the variables defined. 
```{r}
# create an average profile of yes person

# remove OBS column
Yes_profil<- YES_GC %>% 
  select("CHK_ACCT", "DURATION", "HISTORY", "NEW_CAR", "USED_CAR", "FURNITURE", "RADIO_TV", "EDUCATION", "RETRAINING", "AMOUNT", "SAV_ACCT", "EMPLOYMENT", "INSTALL_RATE", "MALE_DIV", "MALE_SINGLE", "MALE_MAR_or_WID", "CO_APPLICANT", "GUARANTOR", "PRESENT_RESIDENT", "REAL_ESTATE", "PROP_UNKN_NONE", "AGE", "OTHER_INSTALL", "RENT", "OWN_RES", "NUM_CREDITS", "JOB", "NUM_DEPENDENTS", "TELEPHONE", "FOREIGN")

#Yes_profil <- data.frame(Yes_profil)
#Yes_profil <- apply(as.matrix.noquote(Yes_profil),2,as.numeric)

# take the mean of each column
Yes_profil <- summarize_all(Yes_profil, mean) # not yet find a way to use median instead of mean

# show matrix through lolipop plot 
Yes_profil <- data.frame(
  x=c('CHK_ACCT', 'DURATION', 'HISTORY', 'NEW_CAR', 'USED_CAR', 'FURNITURE', 'RADIO_TV', 'EDUCATION', 'RETRAINING', 'AMOUNT', 'SAV_ACCT', 'EMPLOYMENT', 'INSTALL_RATE', 'MALE_DIV', 'MALE_SINGLE', 'MALE_MAR_or_WID', 'CO_APPLICANT', 'GUARANTOR', 'PRESENT_RESIDENT', 'REAL_ESTATE', 'PROP_UNKN_NONE', 'AGE', 'OTHER_INSTALL', 'RENT', 'OWN_RES', 'NUM_CREDITS', 'JOB', 'NUM_DEPENDENTS', 'TELEPHONE', 'FOREIGN'),
  y=abs(rnorm(30))
)
```

The lollipop plot below present the mean profile to be qualified as a good client. From these results, most of them ask for a new car, rent their flat but have real estate. The good client in average has a quite good amount of money and has a guarantor. These results are quite different than what we presented before. 
```{r}
graph_yes_profil <- ggplot(Yes_profil, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=x, y=0, yend=y), color="skyblue") +
  geom_point( color="blue", size=4, alpha=0.6) +
  labs(
  title = "Mean of a YES profils",
  y = "Value", x = "Variables name"
)+
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank() 
)

graph_yes_profil

#barplot(prop.table(Yes_profil) * 100, horiz=TRUE, main = "Relative frequency (%)", col = rainbow(3))
```

The following plot shows a selection of the most important variables of our dataframe.
The two main disadvantages of these methods are: The increasing overfitting risk when the number of observations is insufficient. The significant computation time when the number of variables is large.

The result below displays that we seem to have 6 relevant variables: checking the account, the duration of the credit asked, the history of previous credits, the savings, the amount of money owned by the applicant and the real estate owned. 
```{r}
library(mlbench)
library(caret)

# transform table in matrix
GermanCredit <- data.frame(GermanCredit)
GermanCredit <- apply(as.matrix.noquote(GermanCredit),2,as.numeric)

# select important variables
control <- trainControl(method="repeatedcv", number=10, repeats=2)

# train the model
model <- train(RESPONSE~., data=GermanCredit, method="rpart", preProcess="scale", trControl=control)

# estimate variable importance
importance <- varImp(model, scale=FALSE)

# summarize importance
print(importance)

# plot importance
plot(importance)

# comment: we should find a way to print only positive results or to print only 10 firsts variables. 
```


