# Data understanding and preparation

```{r setup, include = FALSE}
source(here::here("script/setup.R"))
```

## Dataset

```{r, warning = FALSE}
# Upload the data
setwd(here::here("data/"))
GermanCreditRaw <- read_csv2("GermanCredit.csv")
```

To create a model that will predict whether a client application represents a risk or not, we work on a dataset from our client containing data on `r nrow(GermanCreditRaw)` past credit applications, described by the following variables:

- **CHK_ACCT**: The checking account status of the applicant in Deutsche Mark (DM).

- **DURATION**: The duration of the credit in months.

- **HISTORY**: The credit history of the applicant.

- **NEW_CAR**: Purpose of the credit.

- **USED_CAR**: Purpose of the credit.

- **FURNITURE**: Purpose of the credit.

- **RADIO/TV**: Purpose of the credit.

- **EDUCATION**: Purpose of the credit.

- **RETRAINING**: Purpose of the credit.

- **AMOUNT**: The credit amount.

- **SAV_ACCT**: The average balance in savings account in Deutsche Mark (DM).

- **EMPLOYMENT**: If the applicant is employed and since how long.

- **INSTALL_RATE**: The installment rate as percentage of disposable income.

- **MALE_DIV**: If the applicant is male and divorced.

- **MALE_SINGLE**: If the applicant is male and single.

- **MALE_MAR_or_WID**: If the applicant is male, married or widowed.

- **CO_APPLICANT**: If the applicant has a co-applicant.

- **GUARANTOR**: If the applicant has a guarantor.

- **PRESENT_RESIDENT**: If the applicant is a resident and since how many years.

- **REAL_ESTATE**: If the applicant owns real estate.

- **PROP-UNKN-NONE**: If the applicant owns no property (or unknown).

- **AGE**: Age of the applicant.

- **OTHER_INSTALL**: If the applicant has other installment plan credit.

- **RENT**: If the applicant rents.

- **OWN_RES**: If the applicant owns residence.

- **NUM_CREDITS**: Number of existing credits of the applicant at our client bank.

- **JOB**: The nature of the applicant's job.

- **NUM_DEPENDENT**: Number of people for whom liable to provide maintenance.

- **TELEPHONE**: If the applicant has a phone in his or her name.

- **FOREIGN**: If the applicant is a foreign worker.

- **RESPONSE**: If the credit application is rated as "Good" or "Bad".

## Exploratory Data Analysis

In this part, we thoroughly explore the dataset to get a better understanding.

### Inacurracies

By doing an exploratory data analysis, we find some inaccuracies and in agreement with our client, we change them as follow:

- One observation of the variable "AGE": 75 instead of 125 years old.
- One observation of the variable "EDUCATION": 1 instead of -1.
- One observation of the variable "GUARANTOR": 1 instead of 2.

```{r}
# Removing the first column, aka "OBS#", because not useful.
GermanCredit <- GermanCreditRaw %>% 
  select(-c("OBS#"))

# Renaming the variables:
names(GermanCredit)[names(GermanCredit) == 'RADIO/TV'] <- 'RADIO_TV'
names(GermanCredit)[names(GermanCredit) == 'CO-APPLICANT'] <- 'CO_APPLICANT'
```

```{r}
# First inaccuracy: one observation of the column age is miscoded.
GermanCredit <- GermanCredit %>% 
  mutate(AGE = replace(AGE, AGE == 125, 75))

# Second inaccuracy: one observation of the column education is miscoded
GermanCredit <- GermanCredit %>% 
  mutate(EDUCATION = replace(EDUCATION, EDUCATION == -1, 1))

# Third inaccuracy: one observation of the column guarantor is miscoded
GermanCredit <- GermanCredit %>% 
  mutate(GUARANTOR = replace(GUARANTOR, GUARANTOR == 2, 1))
```

```{r}
# GermanCredit accepted
YES_GC <- filter(GermanCredit,RESPONSE=="1")
```

```{r}
# GermanCredit refused
NO_GC <- filter(GermanCredit,RESPONSE=="0")
```

### Unbalanced observations

One interesting point is that the dataset is heavily unbalanced: 700 credit applications rated as good versus 300 credit applications rated as bad. We will need to balance the dataset for our modelling.

```{r, echo = FALSE, results = 'hide'}
table(GermanCredit$RESPONSE)
```

```{r, message=FALSE}
# Distribution of the grade per credit applications
GermanCredit %>% 
  ggplot(aes(x = as.factor(RESPONSE), fill=as.factor(RESPONSE))) +
  geom_bar() +
  labs(title = "Number of credit applications per grade",
       y = "Number",
       x = "Grade") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, results = 'hide'}
# Distribution of the continuous variables, i.e. duration, amount, age

# Here duration

p.duration <- GermanCredit %>% 
  ggplot(aes(x = DURATION, y = as.factor(RESPONSE), fill = as.factor(RESPONSE))) +
  geom_boxplot() +
  labs(title = "Duration of the credit applications per grade",
       x = "Months",
       y = "Grade") +
  scale_y_discrete(label=c("0"="No", "1"="Yes")) +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# Amount

p.amount <- GermanCredit %>% 
  ggplot(aes(x = AMOUNT, y = as.factor(RESPONSE), fill=as.factor(RESPONSE))) +
  geom_boxplot() +
  labs(title = "Amount of the credit applications per grade",
       x = "DM",
       y = "Grade") +
  scale_y_discrete(label=c("0"="No", "1"="Yes")) +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# Age

p.age <- GermanCredit %>% 
  ggplot(aes(x = AGE, y = as.factor(RESPONSE), fill=as.factor(RESPONSE))) +
  geom_boxplot() +
  labs(title = "Age of the credit applicants",
       x = "Years",
       y = "Grade") +
  scale_y_discrete(label=c("0"="No", "1"="Yes")) +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, fig.show='hide'}
figure1 <- ggarrange(p.duration, p.age, p.amount,
                    labels = c("A", "B", "C"),
                    ncol = 2, nrow = 2)
figure1
```

```{r}
# Let's explore the distribution of the categorical variables
#CHK_ACCT
p.chkacct <- GermanCredit %>% 
  ggplot(aes(x = CHK_ACCT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Status of the checking account per grade",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#HISTORY
p.history <- GermanCredit %>% 
  ggplot(aes(x = HISTORY, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grades related to the history of past credits",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# SAV_ACCT
p.savacct <- GermanCredit %>% 
  ggplot(aes(x = SAV_ACCT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grades in regard with the average balance in saving accounts",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#NUM_CREDIT
p.numcre <- GermanCredit %>% 
  ggplot(aes(x = NUM_CREDITS, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to the number of credits",
       x = "Number of credits",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, fig.show='hide'}
figure_fin <- ggarrange(p.history, p.savacct, p.numcre, p.chkacct,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_fin
```


```{r}
# Now let's have a look at the binary variables

# NEW_CAR
p_newcar <- GermanCredit %>% 
  ggplot(aes(x = as.factor(NEW_CAR), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a new car",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# USED CAR
p_usedcar <- GermanCredit %>% 
  ggplot(aes(x = as.factor(USED_CAR), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a used car",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# FURNITURE
p_fur <- GermanCredit %>% 
  ggplot(aes(x = as.factor(FURNITURE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a furniture",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# RADIO/TV
p_radtv <- GermanCredit %>% 
  ggplot(aes(x = as.factor(RADIO_TV), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a radio/tv",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, fig.show='hide'}
figure_prod <- ggarrange(p_newcar, p_usedcar, p_fur, p_radtv,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_prod
```

```{r}
# EMPLOYMENT
p.empl <- GermanCredit %>% 
  ggplot(aes(x = EMPLOYMENT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade with regard to employment duration",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#JOB
p.job <- GermanCredit %>% 
  ggplot(aes(x = JOB, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to the nature of jobs",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# EDUCATION
p_edu <- GermanCredit %>% 
  ggplot(aes(x = as.factor(EDUCATION), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for education",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# RETRAINING
p_ret <- GermanCredit %>% 
  ggplot(aes(x = as.factor(RETRAINING), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for retraining",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, fig.show='hide'}
figure_pro <- ggarrange(p.empl, p.job, p_edu, p_ret,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_pro
```


```{r}
# PRESENT_RESIDENTS
p.preres <- GermanCredit %>% 
  ggplot(aes(x = PRESENT_RESIDENT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to residents duration stays",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# INSTALLMENT_RATE
p.insrat <- GermanCredit %>% 
  ggplot(aes(x = INSTALL_RATE, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade per installment rate",
       x = "% of disposable income",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#REAL ESTATE
p_reaest <- GermanCredit %>% 
  ggplot(aes(x = as.factor(REAL_ESTATE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if own real estate",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#PROP_UNKN_NONE
p_prop <- GermanCredit %>% 
  ggplot(aes(x = as.factor(PROP_UNKN_NONE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if own no property or unknown",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#OWN_RES
p_ownres <- GermanCredit %>% 
  ggplot(aes(x = as.factor(OWN_RES), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if owns residence",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#GUARANTOR
p_gua <- GermanCredit %>% 
  ggplot(aes(x = as.factor(GUARANTOR), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if guarantor",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# APPLICANT RENTS
p_apprent <- GermanCredit %>% 
  ggplot(aes(x = as.factor(RENT), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if rent",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, fig.show='hide'}
figure_reales <- ggarrange(p.preres, p.insrat, p_reaest, p_prop, p_ownres, p_gua, p_apprent,
                    labels = c("A", "B", "C", "D", "E", "F", "G"),
                    ncol = 2, nrow = 2)
figure_reales
```

```{r}
# MALE_DIV
p_maldiv <- GermanCredit %>% 
  ggplot(aes(x = as.factor(MALE_DIV), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if male and divorced",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#MALE_SINGLE
p_malsin <- GermanCredit %>% 
  ggplot(aes(x = as.factor(MALE_SINGLE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if male and single",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# MALE_MAR_or_WID
p_malmarwid <- GermanCredit %>% 
  ggplot(aes(x = as.factor(MALE_MAR_or_WID), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if male married or widowed",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#FOREIGN
p_for <- GermanCredit %>% 
  ggplot(aes(x = as.factor(FOREIGN), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if foreign workers",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

```

```{r, fig.show='hide'}
figure_demo <- ggarrange(p_maldiv, p_malsin, p_malmarwid, p_for,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_demo
```

```{r}
#CO APLLICANT
p_coapp <- GermanCredit %>% 
  ggplot(aes(x = as.factor(CO_APPLICANT), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if co-applicant",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#OTHER INSTALL
p_otherinstall <- GermanCredit %>% 
  ggplot(aes(x = as.factor(OTHER_INSTALL), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if other installment plan",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#NUM_DEPENDENT
p.numdep <- GermanCredit %>% 
  ggplot(aes(x = as.factor(NUM_DEPENDENTS), fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to the number of dependent",
       x = "Number of people for whom liable to provide maintenance",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#TELEPHONE
p_tel <- GermanCredit %>% 
  ggplot(aes(x = as.factor(TELEPHONE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if telephone on his name",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, fig.show='hide'}
figure_other <- ggarrange(p_coapp, p_otherinstall,p.numdep, p_tel,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_other
```
```{r, results='hide'}
setwd(here::here("data/"))
write_csv(GermanCredit, "GermanCreditClean.csv")
```

```{r, include=FALSE}
# let's check if old people have basically more credit than young people
mean_yes<-mean(YES_GC$AGE)
mean_yes

mean_no<-mean(NO_GC$AGE)
mean_no

# age does not seem to be a key criterion 
```


```{r}
# correlation matrix

#head(YES_GC)
#corgc <- cor(GermanCredit)
#corgc

#creation of a new dataset
cordata_fin <- GermanCredit[, c("CHK_ACCT", "HISTORY", "AMOUNT", "SAV_ACCT", "NUM_CREDITS", "RESPONSE") ] 
ggpairs(cordata_fin, title="Correlogram on financial data")

cordata_own <- GermanCredit[, c("NEW_CAR", "USED_CAR", "FURNITURE", "RADIO_TV", "RESPONSE") ]
ggpairs(cordata_own, title="Correlogram on owned products data")

cordata_pro <- GermanCredit[, c("JOB", "EDUCATION", "RETRAINING", "EMPLOYMENT", "RESPONSE") ] 
ggpairs(cordata_pro, title="Correlogram on professional data")

cordata_immo <- GermanCredit[, c("INSTALL_RATE", "REAL_ESTATE", "PRESENT_RESIDENT", "PROP_UNKN_NONE", "RENT", "OWN_RES", "RESPONSE") ]
ggpairs(cordata_immo, title="Correlogram on real estate data")

cordata_demo <- GermanCredit[, c("MALE_DIV", "MALE_SINGLE", "MALE_MAR_or_WID", "AGE", "FOREIGN", "RESPONSE") ] 
ggpairs(cordata_demo, title="Correlogram on demographic data")

#cor<-ggpairs(GermanCredit, title="correlogram with ggpairs()") 
```

```{r}
# create an average profile of yes person

# remove OBS column
Yes_profil<- YES_GC %>% 
  select("CHK_ACCT", "DURATION", "HISTORY", "NEW_CAR", "USED_CAR", "FURNITURE", "RADIO_TV", "EDUCATION", "RETRAINING", "AMOUNT", "SAV_ACCT", "EMPLOYMENT", "INSTALL_RATE", "MALE_DIV", "MALE_SINGLE", "MALE_MAR_or_WID", "CO_APPLICANT", "GUARANTOR", "PRESENT_RESIDENT", "REAL_ESTATE", "PROP_UNKN_NONE", "AGE", "OTHER_INSTALL", "RENT", "OWN_RES", "NUM_CREDITS", "JOB", "NUM_DEPENDENTS", "TELEPHONE", "FOREIGN")

#Yes_profil <- data.frame(Yes_profil)
#Yes_profil <- apply(as.matrix.noquote(Yes_profil),2,as.numeric)

# take the mean of each column
Yes_profil <- summarize_all(Yes_profil, mean) # not yet find a way to use median instead of mean

# show matrix through lolipop plot 
Yes_profil <- data.frame(
  x=c('CHK_ACCT', 'DURATION', 'HISTORY', 'NEW_CAR', 'USED_CAR', 'FURNITURE', 'RADIO_TV', 'EDUCATION', 'RETRAINING', 'AMOUNT', 'SAV_ACCT', 'EMPLOYMENT', 'INSTALL_RATE', 'MALE_DIV', 'MALE_SINGLE', 'MALE_MAR_or_WID', 'CO_APPLICANT', 'GUARANTOR', 'PRESENT_RESIDENT', 'REAL_ESTATE', 'PROP_UNKN_NONE', 'AGE', 'OTHER_INSTALL', 'RENT', 'OWN_RES', 'NUM_CREDITS', 'JOB', 'NUM_DEPENDENTS', 'TELEPHONE', 'FOREIGN'),
  y=abs(rnorm(30))
)
```

```{r}
graph_yes_profil <- ggplot(Yes_profil, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=x, y=0, yend=y), color="skyblue") +
  geom_point( color="blue", size=4, alpha=0.6) +
  labs(
  title = "Mean of a YES profils",
  y = "Variables name", x = "Value"
)+
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank() 
)

graph_yes_profil

#barplot(prop.table(Yes_profil) * 100, horiz=TRUE, main = "Relative frequency (%)", col = rainbow(3))
```

The following plot shows a selection of the most important variables of our dataframe.
The two main disadvantages of these methods are: The increasing overfitting risk when the number of observations is insufficient. The significant computation time when the number of variables is large.
```{r}
library(mlbench)
library(caret)

# transform table in matrix
GermanCredit <- data.frame(GermanCredit)
GermanCredit <- apply(as.matrix.noquote(GermanCredit),2,as.numeric)

# select important variables
control <- trainControl(method="repeatedcv", number=10, repeats=2)

# train the model
model <- train(RESPONSE~., data=GermanCredit, method="rpart", preProcess="scale", trControl=control)

# estimate variable importance
importance <- varImp(model, scale=FALSE)

# summarize importance
print(importance)

# plot importance
plot(importance)

# comment: we should find a way to print only positive results or to print only 10 firsts variables. 
```


