# Data understanding and preparation

```{r setup, include = FALSE}
source(here::here("script/setup.R"))
```

## Dataset

```{r, warning = FALSE}
# Upload the data
setwd(here::here("data/"))
GermanCreditRaw <- read_csv2("GermanCredit.csv")
```

To create a model that will predict whether a client application represents a risk or not, we worked on a data set from our client containing data on `r nrow(GermanCreditRaw)` past credit applications, described by the following variables:

- **CHK_ACCT**: The checking account status of the applicant in Deutsche Mark (DM).

- **DURATION**: The duration of the credit in months.

- **HISTORY**: The credit history of the applicant.

- **NEW_CAR**: Purpose of the credit.

- **USED_CAR**: Purpose of the credit.

- **FURNITURE**: Purpose of the credit.

- **RADIO/TV**: Purpose of the credit.

- **EDUCATION**: Purpose of the credit.

- **RETRAINING**: Purpose of the credit.

- **AMOUNT**: The credit amount.

- **SAV_ACCT**: The average balance in savings account in Deutsche Mark (DM).

- **EMPLOYMENT**: If the applicant is employed and since how long.

- **INSTALL_RATE**: The installment rate as percentage of disposable income.

- **MALE_DIV**: If the applicant is male and divorced.

- **MALE_SINGLE**: If the applicant is male and single.

- **MALE_MAR_or_WID**: If the applicant is male, married or widowed.

- **CO_APPLICANT**: If the applicant has a co-applicant.

- **GUARANTOR**: If the applicant has a guarantor.

- **PRESENT_RESIDENT**: If the applicant is a resident and since how many years.

- **REAL_ESTATE**: If the applicant owns real estate.

- **PROP-UNKN-NONE**: If the applicant owns no property (or unknown).

- **AGE**: Age of the applicant.

- **OTHER_INSTALL**: If the applicant has other installment plan credit.

- **RENT**: If the applicant rents.

- **OWN_RES**: If the applicant owns residence.

- **NUM_CREDITS**: Number of existing credits of the applicant at our client bank.

- **JOB**: The nature of the applicant's job.

- **NUM_DEPENDENT**: Number of people for whom liable to provide maintenance.

- **TELEPHONE**: If the applicant has a phone in his or her name.

- **FOREIGN**: If the applicant is a foreign worker.

- **RESPONSE**: If the credit application is rated as "Good" or "Bad".


## Exploratory Data Analysis

In this part, we thoroughly explored the data set to get a better understanding. The goal of the exploratory data analysis was to observe and interpret our data thanks to visualization methods, like plots.  

### Inacurracies

By doing an exploratory data analysis, we found some inaccuracies and in agreement with our client, we changed them as follow:

- One observation of the variable "AGE": 75 instead of 125 years old.
- One observation of the variable "EDUCATION": 1 instead of -1.
- One observation of the variable "GUARANTOR": 1 instead of 2.

```{r}
# Removing the first column, aka "OBS#", because not useful.
GermanCredit <- GermanCreditRaw %>% 
  select(-c("OBS#"))

# Renaming the variables:
names(GermanCredit)[names(GermanCredit) == 'RADIO/TV'] <- 'RADIO_TV'
names(GermanCredit)[names(GermanCredit) == 'CO-APPLICANT'] <- 'CO_APPLICANT'
```

```{r}
# First inaccuracy: one observation of the column age is miscoded.
GermanCredit <- GermanCredit %>% 
  mutate(AGE = replace(AGE, AGE == 125, 75))

# Second inaccuracy: one observation of the column education is miscoded
GermanCredit <- GermanCredit %>% 
  mutate(EDUCATION = replace(EDUCATION, EDUCATION == -1, 1))

# Third inaccuracy: one observation of the column guarantor is miscoded
GermanCredit <- GermanCredit %>% 
  mutate(GUARANTOR = replace(GUARANTOR, GUARANTOR == 2, 1))
```

### Unbalanced observations

To start, we noticed an important point to consider: the data set is heavily unbalanced. As you can see on the following plot, it contains 700 credit applications rated as good versus 300 credit applications rated as bad. We will need to balance the data set for our modelling. 

```{r, echo = FALSE, results = 'hide'}
table(GermanCredit$RESPONSE)
```

<br>

```{r, message=FALSE}
# Distribution of the grade per credit applications
GermanCredit %>% 
  ggplot(aes(x = as.factor(RESPONSE), fill=as.factor(RESPONSE))) +
  geom_bar() +
  labs(title = "Number of credit applications per grade",
       y = "Number",
       x = "Grade") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

<br>

Taking the last point into account, we also decided to split the database in 2 parts: the first part considered only the good clients, and the second part considered only the bad clients. This will help us to study the particularities of each profile.

```{r}
# GermanCredit accepted
YES_GC <- filter(GermanCredit,RESPONSE=="1")
```

```{r}
# GermanCredit refused
NO_GC <- filter(GermanCredit,RESPONSE=="0")
```

### Visualization 

We chose to show some specifics variables as they are the ones we will be using in the modelling part.

To have a better visualization of our variables. We used some box plots or histograms showing the distribution of the data.

```{r, results = 'hide'}
# Distribution of the continuous variables, i.e. duration, amount, age

# Here duration

p.duration <- GermanCredit %>% 
  ggplot(aes(x = DURATION, y = as.factor(RESPONSE), fill = as.factor(RESPONSE))) +
  geom_boxplot() +
  labs(title = "Duration of the credit applications per grade",
       x = "Months",
       y = "Grade") +
  scale_y_discrete(label=c("0"="Bad", "1"="Good")) +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# Amount

p.amount <- GermanCredit %>% 
  ggplot(aes(x = AMOUNT, y = as.factor(RESPONSE), fill=as.factor(RESPONSE))) +
  geom_boxplot() +
  labs(title = "Amount of the credit applications per grade",
       x = "DM",
       y = "Grade") +
  scale_y_discrete(label=c("0"="Bad", "1"="Good")) +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# Age

p.age <- GermanCredit %>% 
  ggplot(aes(x = AGE, y = as.factor(RESPONSE), fill=as.factor(RESPONSE))) +
  geom_boxplot() +
  labs(title = "Age of the credit applicants",
       x = "Years",
       y = "Grade") +
  scale_y_discrete(label=c("0"="Bad", "1"="Good")) +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

<br>

```{r}
figure1 <- ggarrange(p.duration, p.amount,
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2)
figure1
```

<br>

This first box plot A shows that bad clients mostly asked for longer duration credit than good clients. This could be a reason why they received a refusal. The second box plot B shows that most of the good clients asked for a smaller amount. 

Then, we explored the distribution of the financial variables:

```{r}
# Let's explore the distribution of the categorical variables
#CHK_ACCT
p.chkacct <- GermanCredit %>% 
  ggplot(aes(x = CHK_ACCT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Status of the checking account per grade",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#HISTORY
p.history <- GermanCredit %>% 
  ggplot(aes(x = HISTORY, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grades related to the history of past credits",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# SAV_ACCT
p.savacct <- GermanCredit %>% 
  ggplot(aes(x = SAV_ACCT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grades in regard with the average balance in saving accounts",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#NUM_CREDIT
p.numcre <- GermanCredit %>% 
  ggplot(aes(x = NUM_CREDITS, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to the number of credits",
       x = "Number of credits",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

<br>

```{r}
figure_fin <- ggarrange(p.history, p.savacct,
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2)
figure_fin
```

```{r}
figure_fin <- ggarrange(p.numcre, p.chkacct,
                    labels = c("C", "D"),
                    ncol = 1, nrow = 2)
figure_fin
```

<br>

The first graph A represents the situation with past credits. The behavior for good and bad clients is almost the same which does not allow us to make a clear difference. On the graph B we can see that most of the clients have small savings or even no savings at all. Most of the clients have already 1 or 2 credits at this bank. Almost none of them ask for a third or fourth credit. 
On the histogram D we see that the amount of money on the account not so important. Indeed, most of the good client do not even have a checking account. 

```{r}
# NEW_CAR
p_newcar <- GermanCredit %>% 
  ggplot(aes(x = as.factor(NEW_CAR), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a new car",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# USED CAR
p_usedcar <- GermanCredit %>% 
  ggplot(aes(x = as.factor(USED_CAR), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a used car",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# FURNITURE
p_fur <- GermanCredit %>% 
  ggplot(aes(x = as.factor(FURNITURE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a furniture",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# RADIO/TV
p_radtv <- GermanCredit %>% 
  ggplot(aes(x = as.factor(RADIO_TV), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a radio/tv",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, results='hide', include=FALSE}
figure_prod <- ggarrange(p_newcar, p_usedcar, p_fur, p_radtv,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_prod
```

```{r}
# EMPLOYMENT
p.empl <- GermanCredit %>% 
  ggplot(aes(x = EMPLOYMENT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade with regard to employment duration",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#JOB
p.job <- GermanCredit %>% 
  ggplot(aes(x = JOB, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to the nature of jobs",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# EDUCATION
p_edu <- GermanCredit %>% 
  ggplot(aes(x = as.factor(EDUCATION), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for education",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# RETRAINING
p_ret <- GermanCredit %>% 
  ggplot(aes(x = as.factor(RETRAINING), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for retraining",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, results='hide', include=FALSE}
figure_pro <- ggarrange(p.empl, p.job, p_edu, p_ret,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_pro
```

```{r, echo = FALSE}
# PRESENT_RESIDENTS
p.preres <- GermanCredit %>% 
  ggplot(aes(x = PRESENT_RESIDENT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to residents duration stays",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# INSTALLMENT_RATE
p.insrat <- GermanCredit %>% 
  ggplot(aes(x = INSTALL_RATE, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade per installment rate",
       x = "% of disposable income",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#REAL ESTATE
p_reaest <- GermanCredit %>% 
  ggplot(aes(x = as.factor(REAL_ESTATE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if own real estate",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#PROP_UNKN_NONE
p_prop <- GermanCredit %>% 
  ggplot(aes(x = as.factor(PROP_UNKN_NONE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if own no property or unknown",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#OWN_RES
p_ownres <- GermanCredit %>% 
  ggplot(aes(x = as.factor(OWN_RES), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if owns residence",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#GUARANTOR
p_gua <- GermanCredit %>% 
  ggplot(aes(x = as.factor(GUARANTOR), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if guarantor",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# APPLICANT RENTS
p_apprent <- GermanCredit %>% 
  ggplot(aes(x = as.factor(RENT), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if rent",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, results='hide', include=FALSE}
figure_reales1 <- ggarrange(p.preres, p.insrat, p_reaest, p_prop, p_ownres, p_gua, p_apprent,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_reales1
```

```{r, results='hide', include=FALSE}
figure_reales2 <- ggarrange(p_ownres, p_gua, p_apprent,
                    labels = c("E", "F", "G"),
                    ncol = 2, nrow = 2)
figure_reales2
```

```{r}
# MALE_DIV
p_maldiv <- GermanCredit %>% 
  ggplot(aes(x = as.factor(MALE_DIV), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if male and divorced",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#MALE_SINGLE
p_malsin <- GermanCredit %>% 
  ggplot(aes(x = as.factor(MALE_SINGLE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if male and single",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

# MALE_MAR_or_WID
p_malmarwid <- GermanCredit %>% 
  ggplot(aes(x = as.factor(MALE_MAR_or_WID), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if male married or widowed",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#FOREIGN
p_for <- GermanCredit %>% 
  ggplot(aes(x = as.factor(FOREIGN), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if foreign workers",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

```

```{r, results='hide', include=FALSE}
figure_demo <- ggarrange(p_maldiv, p_malsin, p_malmarwid, p_for,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_demo
```

```{r}
#CO APLLICANT
p_coapp <- GermanCredit %>% 
  ggplot(aes(x = as.factor(CO_APPLICANT), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if co-applicant",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#OTHER INSTALL
p_otherinstall <- GermanCredit %>% 
  ggplot(aes(x = as.factor(OTHER_INSTALL), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if other installment plan",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#NUM_DEPENDENT
p.numdep <- GermanCredit %>% 
  ggplot(aes(x = as.factor(NUM_DEPENDENTS), fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to the number of dependent",
       x = "Number of people for whom liable to provide maintenance",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#TELEPHONE
p_tel <- GermanCredit %>% 
  ggplot(aes(x = as.factor(TELEPHONE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if telephone on his name",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r, results='hide', include=FALSE}
figure_other <- ggarrange(p_coapp, p_otherinstall,p.numdep, p_tel,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_other
```

```{r, results='hide'}
setwd(here::here("data/"))
write_csv(GermanCredit, "GermanCreditClean.csv")
```

```{r, include=FALSE}
# let's check if old people have basically more credit than young people
mean_yes<-mean(YES_GC$AGE)
mean_yes

mean_no<-mean(NO_GC$AGE)
mean_no

# age does not seem to be a key criterion 
```

```{r, results='hide', include=FALSE}
# correlation matrix

#head(YES_GC)
#corgc <- cor(GermanCredit)
#corgc

#creation of a new dataset
cordata_fin <- GermanCredit[, c("CHK_ACCT", "HISTORY", "AMOUNT", "SAV_ACCT", "NUM_CREDITS", "RESPONSE") ] 
ggpairs(cordata_fin, title="1. Correlogram on financial data")

cordata_own <- GermanCredit[, c("NEW_CAR", "USED_CAR", "FURNITURE", "RADIO_TV", "RESPONSE") ]
ggpairs(cordata_own, title="2. Correlogram on owned products data")

cordata_pro <- GermanCredit[, c("JOB", "EDUCATION", "RETRAINING", "EMPLOYMENT", "RESPONSE") ] 
ggpairs(cordata_pro, title="3. Correlogram on professional data")

cordata_immo <- GermanCredit[, c("INSTALL_RATE", "REAL_ESTATE", "PRESENT_RESIDENT", "PROP_UNKN_NONE", "RENT", "OWN_RES", "RESPONSE") ]
ggpairs(cordata_immo, title="4. Correlogram on real estate data")

cordata_demo <- GermanCredit[, c("MALE_DIV", "MALE_SINGLE", "MALE_MAR_or_WID", "AGE", "FOREIGN", "RESPONSE") ] 
ggpairs(cordata_demo, title="5. Correlogram on demographic data")

#cor<-ggpairs(GermanCredit, title="correlogram with ggpairs()") 
```

### Profile of a good client

The following part of the project is focus on defining a typical profile of a good client. The goal is to define an average good client based on the average of all the variables defined. 

First, we cleaned the data set created at the beginning which contain only good clients to have the average of each variable. Then, we created a plot with these average data.
```{r}
# create an average profile of yes person

# remove OBS column
Yes_profil<- YES_GC %>% 
  select("CHK_ACCT", "DURATION", "HISTORY", "NEW_CAR", "USED_CAR", "FURNITURE", "RADIO_TV", "EDUCATION", "RETRAINING", "AMOUNT", "SAV_ACCT", "EMPLOYMENT", "INSTALL_RATE", "MALE_DIV", "MALE_SINGLE", "MALE_MAR_or_WID", "CO_APPLICANT", "GUARANTOR", "PRESENT_RESIDENT", "REAL_ESTATE", "PROP_UNKN_NONE", "AGE", "OTHER_INSTALL", "RENT", "OWN_RES", "NUM_CREDITS", "JOB", "NUM_DEPENDENTS", "TELEPHONE", "FOREIGN")

#Yes_profil <- data.frame(Yes_profil)
#Yes_profil <- apply(as.matrix.noquote(Yes_profil),2,as.numeric)

# take the mean of each column
Yes_profil <- summarize_all(Yes_profil, mean) # not yet find a way to use median instead of mean

# show matrix through lolipop plot 
Yes_profil <- data.frame(
  x=c('CHK_ACCT', 'DURATION', 'HISTORY', 'NEW_CAR', 'USED_CAR', 'FURNITURE', 'RADIO_TV', 'EDUCATION', 'RETRAINING', 'AMOUNT', 'SAV_ACCT', 'EMPLOYMENT', 'INSTALL_RATE', 'MALE_DIV', 'MALE_SINGLE', 'MALE_MAR_or_WID', 'CO_APPLICANT', 'GUARANTOR', 'PRESENT_RESIDENT', 'REAL_ESTATE', 'PROP_UNKN_NONE', 'AGE', 'OTHER_INSTALL', 'RENT', 'OWN_RES', 'NUM_CREDITS', 'JOB', 'NUM_DEPENDENTS', 'TELEPHONE', 'FOREIGN'),
  y=abs(rnorm(30))
)
```

The lollipop plot below represents the mean profile to be qualified as a good client. From these results, most of them asked for a new car, rented their flat but had real estate. The good client in average had a quite good amount of money and had a guarantor. These results are quite different than what we presented before.
s
```{r}
graph_yes_profil <- ggplot(Yes_profil, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=x, y=0, yend=y), color="skyblue") +
  geom_point( color="blue", size=4, alpha=0.6) +
  labs(
  title = "Mean of a good profile",
  y = "Value", x = "Variables name"
)+
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank() 
)

graph_yes_profil

#barplot(prop.table(Yes_profil) * 100, horiz=TRUE, main = "Relative frequency (%)", col = rainbow(3))
```

### Profile of a bad client

Then, we used exactly the same approach to build the typical profile of a bad client and identify the average variables that qualify a bad client in this bank.

```{r}
# create an average profile of yes person

# remove OBS column
No_profil<- NO_GC %>% 
  select("CHK_ACCT", "DURATION", "HISTORY", "NEW_CAR", "USED_CAR", "FURNITURE", "RADIO_TV", "EDUCATION", "RETRAINING", "AMOUNT", "SAV_ACCT", "EMPLOYMENT", "INSTALL_RATE", "MALE_DIV", "MALE_SINGLE", "MALE_MAR_or_WID", "CO_APPLICANT", "GUARANTOR", "PRESENT_RESIDENT", "REAL_ESTATE", "PROP_UNKN_NONE", "AGE", "OTHER_INSTALL", "RENT", "OWN_RES", "NUM_CREDITS", "JOB", "NUM_DEPENDENTS", "TELEPHONE", "FOREIGN")

# take the mean of each column
No_profil <- summarize_all(No_profil, mean) # not yet find a way to use median instead of mean

# show matrix through lolipop plot 
No_profil <- data.frame(
  x=c('CHK_ACCT', 'DURATION', 'HISTORY', 'NEW_CAR', 'USED_CAR', 'FURNITURE', 'RADIO_TV', 'EDUCATION', 'RETRAINING', 'AMOUNT', 'SAV_ACCT', 'EMPLOYMENT', 'INSTALL_RATE', 'MALE_DIV', 'MALE_SINGLE', 'MALE_MAR_or_WID', 'CO_APPLICANT', 'GUARANTOR', 'PRESENT_RESIDENT', 'REAL_ESTATE', 'PROP_UNKN_NONE', 'AGE', 'OTHER_INSTALL', 'RENT', 'OWN_RES', 'NUM_CREDITS', 'JOB', 'NUM_DEPENDENTS', 'TELEPHONE', 'FOREIGN'),
  y=abs(rnorm(30))
)
```

```{r}
graph_no_profil <- ggplot(No_profil, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=x, y=0, yend=y), color="orange") +
  geom_point( color="red", size=4, alpha=0.6) +
  labs(
  title = "Mean of a bag profile",
  y = "Value", x = "Variables name"
)+
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank() 
)

graph_no_profil

```

As we can see on the orange lollipop plot, the result is different. Most of the bad clients rented their flat. This criteria sounds really important to qualify a client. Almost all of them do not have any other credit in the bank and they have other installment plan credits. For further analysis, it will be more relevant to use the median instead of the mean to have more robust results. 
