--- 
title: "Project in Data Analytics for Decision Making"
author: "Manon Verjus and Yooby Gigandet"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---

# Introduction

Our work for the course "Project in Data Analytics for Decision Making" is to predict the credit risk associated to customers for our client, a bank. 

To do so, we used the CRISP-DM method (CRoss Industry Standard Process for Data Mining):

- **Business understanding**: Credit risk is defined as the risk of loss resulting from the failure by a borrower to repay the principal and interest owed to the lender. By performing a credit risk analysis, the lender determines the borrower's ability to meet debt obligations in order to cushion itself from losses. It is therefore important to efficiently classify the risks of the credit applications.

- **Data understanding and preparation**: We work on the `german` dataset. 

- **Modelling**: For this part, we used several models.

- **Evaluation**: 

- **Deployment**:


<!--chapter:end:index.Rmd-->

# Data understanding and preparation

```{r setup, include = FALSE}
source(here::here("script/setup.R"))
```

## Data understanding

```{r, warning = FALSE}
# Upload the data
setwd(here::here("data/"))
GermanCreditRaw <- read_csv2("GermanCredit.csv")
```

To create a model that will predict whether a client application represents a risk or not, we work on a dataset from our client containing data on `r nrow(GermanCreditRaw)` past credit applications, described by the following variables:

- **CHK_ACCT**: The checking account status of the applicant in deutsche Mark (DM).

- **DURATION**: The duration of the credit in months.

- **HISTORY**: The credit history of the applicant.

- **NEW_CAR**: Purpose of the credit.

- **USED_CAR**: Purpose of the credit.

- **FURNITURE**: Purpose of the credit.

- **RADIO/TV**: Purpose of the credit.

- **EDUCATION**: Purpose of the credit.

- **RETRAINING**: Purpose of the credit.

- **AMOUNT**: The credit amount.

- **SAV_ACCT**: The average balance in savings account in deutsche Mark (DM).

- **EMPLOYMENT**: If the applicant is employed and since how long.

- **INSTALL_RATE**: The installment rate as percentage of disposable income.

- **MALE_DIV**: If the applicant is male and divorced.

- **MALE_SINGLE**: If the applicant is male and single.

- **MALE_MAR_or_WID**: If the applicant is male, married or widowed.

- **CO-APPLICANT**: If the applicant has a co-applicant.

- **GUARANTOR**: If the applicant has a guarantor.

- **PRESENT_RESIDENT**: If the applicant is a resident and since how many years.

- **REAL_ESTATE**: If the applicant owns real estate.

- **PROP-UNKN-NONE**: If the applicant owns no property (or unknown).

- **AGE**: Age of the applicant in years.

- **OTHER_INSTALL**: If the applicant has other installment plan credit.

- **RENT**: If the applicant rents.

- **OWN_RES**: If the applicant owns residence.

- **NUM_CREDITS**: Number of existing credits of the applicant at our client bank.

- **JOB**: The nature of the applicant's job.

- **NUM_DEPENDENT**: Number of people for whom liable to provide maintenance.

- **TELEPHONE**: If the applicant has a phone in his or her name.

- **FOREIGN**: If the applicant is a foreign worker.

- **RESPONSE**: If the credit application is rated as "Good" or "Bad".


```{r}
# Removing the first column, aka "OBS#", because it is repetitive
GermanCredit <- GermanCreditRaw %>% 
  select(-c("OBS#"))
```

```{r}
# First inaccuracy: one observation of the column age is miscoded.
GermanCredit <- GermanCredit %>% 
  mutate(AGE = replace(AGE, AGE == 125, 75))

# Second inaccuracy: one observation of the column education is miscoded
GermanCredit <- GermanCredit %>% 
  mutate(EDUCATION = replace(EDUCATION, EDUCATION == -1, 1))

# Third inaccuracy: one observation of the column guarantor is miscoded
GermanCredit <- GermanCredit %>% 
  mutate(GUARANTOR = replace(GUARANTOR, GUARANTOR == 2, 1))

# Fourth inacurracy: the categories are miscoded for the column PRESENT_RESID
GermanCredit <- GermanCredit %>% 
  mutate(PRESENT_RESIDENT = replace(PRESENT_RESIDENT, PRESENT_RESIDENT == 1, 0)) %>% 
  mutate(PRESENT_RESIDENT = replace(PRESENT_RESIDENT, PRESENT_RESIDENT == 2, 1)) %>% 
  mutate(PRESENT_RESIDENT = replace(PRESENT_RESIDENT, PRESENT_RESIDENT == 3, 2)) %>% 
  mutate(PRESENT_RESIDENT = replace(PRESENT_RESIDENT, PRESENT_RESIDENT == 4, 3))
```

```{r}
# Coding as factors the following variables: CHK_ACCT, HISTORY, NEW_CAR, USED_CAR, FURNITURE, RADIO/TV, EDUCATION, RETRAINING, SAV_ACCT, EMPLOYMENT, MALE_DIV, MAL_SINGLE, MALE_MAR_WID, CO-APPLICANT, GUARANTOR, PRESENT_RESIDENT, REAL_ESTATE, PROP_UNKN_NONE, OTHER_INSTALL, RENT, OWN_RES, JOB, TELEPHONE, FOREIGN and RESPONSE.

factor_column <- c("CHK_ACCT", "HISTORY", "NEW_CAR", "USED_CAR", "FURNITURE", "RADIO/TV", "EDUCATION", "RETRAINING", "SAV_ACCT", "EMPLOYMENT", "MALE_DIV", "MALE_SINGLE", "MALE_MAR_or_WID", "CO-APPLICANT", "GUARANTOR", "PRESENT_RESIDENT", "REAL_ESTATE", "PROP_UNKN_NONE", "OTHER_INSTALL", "RENT", "OWN_RES", "JOB", "TELEPHONE", "FOREIGN", "RESPONSE")

GermanCredit[,factor_column] <- lapply(GermanCredit[,factor_column], factor)
```

```{r}
# Write csv file
setwd(here::here("data/"))
write_csv(GermanCredit, "GermanCreditClean.csv")
```

## Exploratory Data Analysis

By exploring the dataset, we find some inaccuracies and in agreement with the customer, we change them as follow:

- One observation of the column "Age": 75 instead of 125 years old.
- One observation of the column "Education": 1 instead of -1.
- One observation of the column "Guarantor": 1 instead of 2.
- Code the categories of the column "Present_resid": 0 to 3 instead of 1 to 4

```{r, include = FALSE}
setwd(here::here("data/"))
GermanCredit <- read_csv("GermanCreditClean.csv")
```

```{r}
# GermanCredit accepted
YES_GC <- filter(GermanCredit,RESPONSE=="1")
```

```{r}
# GermanCredit refused
NO_GC <- filter(GermanCredit,RESPONSE=="0")
```

The German Credit data is heavily unbalanced: 700 credit applications rated as good versus 300 credit applications rated as bad.

```{r, echo = FALSE, results = 'hide'}
table(GermanCredit$RESPONSE)
```

```{r, message=FALSE}
# Distribution of the grade per credit applications
GermanCredit %>% 
  ggplot(aes(x = as.factor(RESPONSE), fill=as.factor(RESPONSE))) +
  geom_bar() +
  labs(title = "Number of credit applications per grade",
       y = "Number",
       x = "Grade") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="Bad", "1"="Good")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
```

```{r}
# Distribution of the continuous variables, i.e. duration, amount, age
# Here duration

p.duration <- GermanCredit %>% 
  ggplot(aes(x = DURATION, y = as.factor(RESPONSE), fill = as.factor(RESPONSE))) +
  geom_boxplot() +
  labs(title = "Duration of the credit applications per grade",
       x = "Months",
       y = "Grade") +
  scale_y_discrete(label=c("0"="No", "1"="Yes")) +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p.duration

# Nothing to note
```

```{r}
# Same as above, for age

p.age <- GermanCredit %>% 
  ggplot(aes(x = AGE, y = as.factor(RESPONSE), fill=as.factor(RESPONSE))) +
  geom_boxplot() +
  labs(title = "Age of the credit applicants",
       x = "Years",
       y = "Grade") +
  scale_y_discrete(label=c("0"="No", "1"="Yes")) +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p.age

# One outlier to recode - 75 years old instead of 125 years old
```

```{r}
# Same as above, for amount
p.amount <- GermanCredit %>% 
  ggplot(aes(x = AMOUNT, y = as.factor(RESPONSE), fill=as.factor(RESPONSE))) +
  geom_boxplot() +
  labs(title = "Amount of the credit applications per grade",
       x = "DM",
       y = "Grade") +
  scale_y_discrete(label=c("0"="No", "1"="Yes")) +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p.amount

# A lot of outliers for the good applications
```


```{r}
library("ggpubr")

figure1 <- ggarrange(p.duration, p.age, p.amount,
                    labels = c("A", "B", "C"),
                    ncol = 2, nrow = 2)
figure1
```

```{r}
# Let's explore the distribution of the categorical variables
#CHK_ACCT
p.chkacct <- GermanCredit %>% 
  ggplot(aes(x = CHK_ACCT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Status of the checking account per grade",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#p.chkacct

# I didn't achieve to put the labels here for the x-axis
```

What does the first category means? <0, meaning 0? So the account is opened but there is nothing on it?
Another point, if you don't have any checking account, your credit applications has more probability to be rated as good?

```{r}
#HISTORY
p.history <- GermanCredit %>% 
  ggplot(aes(x = HISTORY, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grades related to the history of past credits",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#p.history
```
Here again, seems weird. At 3 and 4, it means the previous credit were not or partially reimbursed. But they are graded as good?

```{r}
# SAV_ACCT
p.savacct <- GermanCredit %>% 
  ggplot(aes(x = SAV_ACCT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grades in regard with the average balance in saving accounts",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#p.savacct
```



```{r}
#NUM_CREDIT
p.numcre <- GermanCredit %>% 
  ggplot(aes(x = NUM_CREDITS, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to the number of credits",
       x = "Number of credits",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#p.numcre
```

```{r}
figure_fin <- ggarrange(p.history, p.savacct, p.numcre, p.chkacct,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_fin
```


```{r}
# Now let's have a look at the binary variables
# NEW_CAR
p_newcar <- GermanCredit %>% 
  ggplot(aes(x = as.factor(NEW_CAR), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a new car",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_newcar
```

```{r}
# USED CAR
p_usedcar <- GermanCredit %>% 
  ggplot(aes(x = as.factor(USED_CAR), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a used car",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_usedcar
```

```{r}
# FURNITURE
p_fur <- GermanCredit %>% 
  ggplot(aes(x = as.factor(FURNITURE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a furniture",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_fur
```

```{r}
# RADIO/TV
p_radtv <- GermanCredit %>% 
  ggplot(aes(x = as.factor('RADIO.TV'), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for a radio/tv",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_radtv
```

```{r}
figure_prod <- ggarrange(p_newcar, p_usedcar, p_fur, p_radtv,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_prod
```


Some questions need to be asked. What's the difference between an application with a small saving accounts and one with none saving accounts? Why the bank gives good grades to the latest?

```{r}
# EMPLOYMENT
p.empl <- GermanCredit %>% 
  ggplot(aes(x = EMPLOYMENT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade with regard to employment duration",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#p.empl
```

```{r}
#JOB
p.job <- GermanCredit %>% 
  ggplot(aes(x = JOB, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to the nature of jobs",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#p.job
```

```{r}
# EDUCATION
p_edu <- GermanCredit %>% 
  ggplot(aes(x = as.factor(EDUCATION), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for education",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_edu

# comment: pourquoi dans celui-ci il a -1 alors que le code est exactement identique? ligne 37 de la colonne EDUCATION du data GermanCredit il y a un -1. Pas normal. It seems to be wrong. 
```

```{r}
# RETRAINING
p_ret <- GermanCredit %>% 
  ggplot(aes(x = as.factor(RETRAINING), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if for retraining",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_ret
```

```{r}
figure_pro <- ggarrange(p.empl, p.job, p_edu, p_ret,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_pro
```


```{r}
# PRESENT_RESIDENTS
p.preres <- GermanCredit %>% 
  ggplot(aes(x = PRESENT_RESIDENT, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to residents duration stays",
       x = "Category",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#p.preres

#Problem here, the categories should be between 0 and 3 but are between 1 and 4.

```

```{r}
# 
p.insrat <- GermanCredit %>% 
  ggplot(aes(x = INSTALL_RATE, fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade per installment rate",
       x = "% of disposable income",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#p.insrat
```

```{r}
#REAL ESTATE
p_reaest <- GermanCredit %>% 
  ggplot(aes(x = as.factor(REAL_ESTATE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if own real estate",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_reaest
```

```{r}
#PROP_UNKN_NONE
p_prop <- GermanCredit %>% 
  ggplot(aes(x = as.factor(PROP_UNKN_NONE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if own no property or unknown",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_prop
```

```{r}
#OWN_RES
p_ownres <- GermanCredit %>% 
  ggplot(aes(x = as.factor(OWN_RES), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if owns residence",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_ownres
```

```{r}
#GUARANTOR
p_gua <- GermanCredit %>% 
  ggplot(aes(x = as.factor(GUARANTOR), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if guarantor",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_gua

#Again, what the 2?

```

```{r}
# APPLICANT RENTS
p_apprent <- GermanCredit %>% 
  ggplot(aes(x = as.factor(RENT), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if rent",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_apprent
```

```{r}
figure_reales <- ggarrange(p.preres, p.insrat, p_reaest, p_prop, p_ownres, p_gua, p_apprent,
                    labels = c("A", "B", "C", "D", "E", "F", "G"),
                    ncol = 2, nrow = 2)
figure_reales
```




```{r}
# MALE_DIV
p_maldiv <- GermanCredit %>% 
  ggplot(aes(x = as.factor(MALE_DIV), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if male and divorced",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_maldiv
```

```{r}
#MALE_SINGLE
p_malsin <- GermanCredit %>% 
  ggplot(aes(x = as.factor(MALE_SINGLE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if male and single",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_malsin
```

```{r}
# MALE_MAR_or_WID
p_malmarwid <- GermanCredit %>% 
  ggplot(aes(x = as.factor(MALE_MAR_or_WID), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if male married or widowed",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_malmarwid
```

```{r}
#FOREIGN
p_for <- GermanCredit %>% 
  ggplot(aes(x = as.factor(FOREIGN), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if foreign workers",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_for
```

```{r}
figure_demo <- ggarrange(p_maldiv, p_malsin, p_malmarwid, p_for,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_demo
```

```{r}
#CO APLLICANT
p_coapp <- GermanCredit %>% 
  ggplot(aes(x = as.factor(`CO-APPLICANT`), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if co-applicant",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_coapp

#This one is also strange, meaning that if there is a co-applicant, it is more rejected? Must be the opposite

```

```{r}
#OTHER INSTALL
p_otherinstall <- GermanCredit %>% 
  ggplot(aes(x = as.factor(OTHER_INSTALL), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if other installment plan",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_otherinstall
```

```{r}
#NUM_DEPENDENT
p.numdep <- GermanCredit %>% 
  ggplot(aes(x = as.factor(NUM_DEPENDENTS), fill=as.factor(RESPONSE)))+
  geom_bar(position = "dodge") +
  labs(title = "Credit grade related to the number of dependent",
       x = "Number of people for whom liable to provide maintenance",
       y = "Number") +
  theme(legend.position="none") +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))
  
#p.numdep
```

```{r}
#TELEPHONE
p_tel <- GermanCredit %>% 
  ggplot(aes(x = as.factor(TELEPHONE), fill = as.factor(RESPONSE))) +
  geom_bar(position = "dodge") +
  labs(title = "Credit grade if telephone on his name",
       x = "",
       y = "Number") +
  theme(legend.position="none") +
  scale_x_discrete(label=c("0"="No", "1"="Yes")) +
  scale_fill_manual(values = alpha(c("red3", "springgreen4"), .5))

#p_tel
```

```{r}
figure_other <- ggarrange(p_coapp, p_otherinstall,p.numdep, p_tel,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2)
figure_other
```


```{r, include=FALSE}
# let's check if old people have basically more credit than young people
mean_yes<-mean(YES_GC$AGE)
mean_yes

mean_no<-mean(NO_GC$AGE)
mean_no

# age does not seem to be a key criterion 
```


```{r}
# correlation matrix

#head(YES_GC)
#corgc <- cor(GermanCredit)
#corgc

#creation of a new dataset
cordata_fin <- GermanCredit[, c("CHK_ACCT", "HISTORY", "AMOUNT", "SAV_ACCT", "NUM_CREDITS", "RESPONSE") ] 
ggpairs(cordata_fin, title="Correlogram on financial data")

cordata_own <- GermanCredit[, c("NEW_CAR", "USED_CAR", "FURNITURE", "RADIO/TV", "RESPONSE") ]
ggpairs(cordata_own, title="Correlogram on owned products data")

cordata_pro <- GermanCredit[, c("JOB", "EDUCATION", "RETRAINING", "EMPLOYMENT", "RESPONSE") ] 
ggpairs(cordata_pro, title="Correlogram on professional data")

cordata_immo <- GermanCredit[, c("INSTALL_RATE", "REAL_ESTATE", "PRESENT_RESIDENT", "PROP_UNKN_NONE", "RENT", "OWN_RES", "RESPONSE") ]
ggpairs(cordata_immo, title="Correlogram on real estate data")

cordata_demo <- GermanCredit[, c("MALE_DIV", "MALE_SINGLE", "MALE_MAR_or_WID", "AGE", "FOREIGN", "RESPONSE") ] 
ggpairs(cordata_demo, title="Correlogram on demographic data")

#cor<-ggpairs(GermanCredit, title="correlogram with ggpairs()") 
```

```{r}
# create an average profile of yes person

# remove OBS column
Yes_profil<- YES_GC %>% 
  select("CHK_ACCT", "DURATION", "HISTORY", "NEW_CAR", "USED_CAR", "FURNITURE", "RADIO/TV", "EDUCATION", "RETRAINING", "AMOUNT", "SAV_ACCT", "EMPLOYMENT", "INSTALL_RATE", "MALE_DIV", "MALE_SINGLE", "MALE_MAR_or_WID", "CO-APPLICANT", "GUARANTOR", "PRESENT_RESIDENT", "REAL_ESTATE", "PROP_UNKN_NONE", "AGE", "OTHER_INSTALL", "RENT", "OWN_RES", "NUM_CREDITS", "JOB", "NUM_DEPENDENTS", "TELEPHONE", "FOREIGN")

#Yes_profil <- data.frame(Yes_profil)
#Yes_profil <- apply(as.matrix.noquote(Yes_profil),2,as.numeric)

# take the mean of each column
Yes_profil <- summarize_all(Yes_profil, mean) # not yet find a way to use median instead of mean

# show matrix through lolipop plot 
Yes_profil <- data.frame(
  x=c('CHK_ACCT', 'DURATION', 'HISTORY', 'NEW_CAR', 'USED_CAR', 'FURNITURE', 'RADIO/TV', 'EDUCATION', 'RETRAINING', 'AMOUNT', 'SAV_ACCT', 'EMPLOYMENT', 'INSTALL_RATE', 'MALE_DIV', 'MALE_SINGLE', 'MALE_MAR_or_WID', 'CO.APPLICANT', 'GUARANTOR', 'PRESENT_RESIDENT', 'REAL_ESTATE', 'PROP_UNKN_NONE', 'AGE', 'OTHER_INSTALL', 'RENT', 'OWN_RES', 'NUM_CREDITS', 'JOB', 'NUM_DEPENDENTS', 'TELEPHONE', 'FOREIGN'),
  y=abs(rnorm(30))
)
```

```{r}
graph_yes_profil <- ggplot(Yes_profil, aes(x=x, y=y)) +
  geom_segment( aes(x=x, xend=x, y=0, yend=y), color="skyblue") +
  geom_point( color="blue", size=4, alpha=0.6) +
  labs(
  title = "Mean of a YES profils",
  y = "Variables name", x = "Value"
)+
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank() 
)

graph_yes_profil

#barplot(prop.table(Yes_profil) * 100, horiz=TRUE, main = "Relative frequency (%)", col = rainbow(3))
```

The following plot shows a selection of the most important variables of our dataframe.
The two main disadvantages of these methods are: The increasing overfitting risk when the number of observations is insufficient. The significant computation time when the number of variables is large.
```{r}
library(mlbench)
library(caret)

# transform table in matrix
GermanCredit <- data.frame(GermanCredit)
GermanCredit <- apply(as.matrix.noquote(GermanCredit),2,as.numeric)

# select important variables
control <- trainControl(method="repeatedcv", number=10, repeats=2)

# train the model
model <- train(RESPONSE~., data=GermanCredit, method="rpart", preProcess="scale", trControl=control)

# estimate variable importance
importance <- varImp(model, scale=FALSE)

# summarize importance
print(importance)

# plot importance
plot(importance)

# comment: we should find a way to print only positive results or to print only 10 firsts variables. 
```

<!--chapter:end:02-Data.Rmd-->

## Trees

```{r}
set.seed(123) # for reproducibility
index.tr <- sample(x=1:nrow(GermanCredit), size=2/3*nrow(GermanCredit), replace=FALSE)
GermanCredit.tr <- GermanCredit[index.tr,]
GermanCredit.te <- GermanCredit[-index.tr,]
```

```{r, include=FALSE}
# Initialise our tree
GermanCreditTree <- rpart(as_factor(RESPONSE)~., data=GermanCredit.tr)
rpart.plot(GermanCreditTree)
```

```{r, include=FALSE}
plotcp(GermanCreditTree)
```

```{r, include=FALSE}
GermanCreditTree.prune <- prune(GermanCreditTree, cp=0.035)
rpart.plot(GermanCreditTree.prune)
```

```{r, include=FALSE}
pred <- predict(GermanCreditTree.prune, newdata=GermanCredit.te, type="class")
table(Pred=pred, Obs=GermanCredit.te$RESPONSE)

predict(GermanCreditTree.prune, newdata=GermanCredit.te, type="prob")
```




<!--chapter:end:03-Trees.Rmd-->

# Models

## Logistic Regression

```{r} 
# Download the cleaned data set
setwd(here::here("data/"))
GermanCredit <- read_csv("GermanCreditClean.csv")
```

We fit a logistic regression to test if it could predict the output we desired.

```{r}
# Creation of a training and a testing data sets

set.seed(234) # to be able to replicate the same training/testing sets
index <- sample(x=c(1,2), size=nrow(GermanCredit), replace=TRUE, prob=c(0.75,0.25)) # 1==training set, 2==test set
GermanCredit.tr <- GermanCredit[index==1,] # Training set
GermanCredit.te <- GermanCredit[index==2,] # Testing set
```

For our first model we'll select all the variables given in the German Credit data set.

```{r}
mod.logr <- glm(as_factor(RESPONSE)~., data = GermanCredit.tr, family="binomial")
summary(mod.logr)
```

Our initial model is therefore:

$$
z_i = a_o + a_1CHKACCT_{1i} + ... + a_{32}Foreign_{1i}
$$

Let's check if we can select better variables for the model

```{r}
# Using the AIC
mod.logr.sel <- step(mod.logr) # Here by default, backwards selection
summary(mod.logr.sel) # Reminder, the lower the AIC the better
```

Predictions: 

```{r}
prob.te <- predict(mod.logr.sel, newdata=GermanCredit.te, type="response")
pred.te <- ifelse(prob.te >= 0.5, 1, 0)
table(Pred=pred.te, Obs=GermanCredit.te$RESPONSE)
```

Not a good model. Do not forget that the prior of this data set is not balanced at all. We should take it into account.

As depicted below, if our model was good, we should have boxplot that are far away from the 0.5, which is not the case, especially for the bad credits.

```{r}
boxplot(prob.te~GermanCredit.te$RESPONSE)
```


<!--chapter:end:04-LogisticRegression.Rmd-->

